Subsegmental language detection in Celtic language text

### 2014-05-09 codeswitch-cltw-2014/codeswitch.tex
methodology
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52722 72bbbca6-d526-0410-a7d9-f06f51895060

>>>>

Once we get the probabilities, our task at hand is to take in the data and process it such that the  sub-segments of code-switched data are detected in it. We collected data from twitter over a period of time and this was filtered into three sets which had been identified to be Irish, Welsh and Breton. To be able to compare with the language model built above in the character n-gram approach, this data is to be processed like it aswell. \\

Since, there were instances of non-standard input in the Twitter data, certain terminologies were escaped, such as mentions (starting with ‘@’), hashtags (#xyz), Re-Tweet (RT) and hyperlinks.\\
This processed data is then given as input to our module which uses heuristics to come up with sub-segment information. \\

Code-Switch Chunking - \\
